### 2020-05-27 sc20_reviews/response.md

We thank the reviewers for their detailed and insightful feedback.

Changes made in response to reviewer comments:

  * Added Section V.G: Load Imbalance.
  * Expanded Section VI: Case Study.

@@

Responding to reviewer questions:

## Reviewer 1

  * Task graphs can be arbitrary, including irregular graphs. We added an example to Figure 1.

  * METG has already proven useful for exposing behaviors at the limits of system performance. We updated Section VI to clarify.

  * **FIXME: Please justify the use of small task granularity values (lower or equal than 1ms).**

## Reviewer 2

## Reviewer 3

## Reviewer 4

## Reviewer 5

### 2020-05-27 6_related.tex
Update related work.

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. The largest study we know of,
for the mini-app LULESH~\cite{LULESH13}, compares 7 programming
systems (Chapel, Charm++, CUDA, Lizst, Loci, OpenMP, and MPI), each of
which require a separate, tuned implementation (in contrast to
Task Bench). Other
studies usually lack a comprehensive evaluation, even if multiple
implementations are available:

>>>>

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. {\color{blue} The largest studies
we know of consider at most 7 and 6 programming systems,
respectively~\cite{LULESH13, Deakin19}, and the latter only considers
on-node programming models.} In both cases, the mini-apps under study
require a separate, tuned implementation (in contrast to Task
Bench). Other studies usually lack a comprehensive evaluation, even if
multiple implementations are available:

%% for the mini-app LULESH~\cite{LULESH13}, compares 7 programming
%% systems (Chapel, Charm++, CUDA, Lizst, Loci, OpenMP, and MPI), each of
%% which

% Deakin19:
%% BabelStream: OpenMP, Kokkos, CUDA, OpenACC, OpenCL
%% TeaLeaf: OpenMP, Kokkos, CUDA, OpenACC
%% CloverLeaf: OpenMP, Kokkos, CUDA, OpenACC, OpenCL
%% Neutral: OpenMP, Kokkos, CUDA, OpenACC, OpenCL
%% MiniFMM: OpenMP, Kokkos, CUDA, OpenCL
